What about children's wellbeing? Framing active school travel in Ontario, Canada

### 2021-04-09 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Cleaning code update and intro paragraph
Slightly updated the corpus cleaning code and added a new paragraph in the intro about CIM study in Canada

In the case of Canada... _review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_

@@

```{r}
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
#corpus <- tm_map(corpus, removeNumbers)

>>>>

In the case of Canada, Riazi found that location, specifically concentration of population, was the stronger correlate to CIM even after accounting for the influence of gender. However whereas European countries have a positive correlation between population density and impendence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city between Quebec City and Montreal. Riazi's team is quick to note that such differences in the Canadian context could be a results of the multicultural diversity in large Canadian cities and thus are sites of very differing social and cultural norms influence the CIM findings. (Missing Reference.bib citations)
_review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_

@@

```{r}
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, content_transformer(tolower))

# Words can also be removed manually by creating a vector of strings 
#NAwords <- c("school", "transportation", "can", "use", "active")
#corpus <- tm_map(corpus, removeWords, NAwords)
#corpus <- tm_map(corpus, removeNumbers)

corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
